Estimating Neighborhood Rents with Scraped Data

### 2018-06-27 manuscript/manuscript.Rmd
adding manuscript.rmd for working on PDF version

The BYM Spatial with AR(1) is the [Besag-York-Mollie (1991)](https://link.springer.com/article/10.1007/BF00116466){target="_blank"} intrinsic conditional autoregressive spatial model with AR(1) and exchangeable hyperparameters for the panel's temporal structure (referred to as `bym` using shorthand). The random-effect $S_i$ is assumed to come from a normal distribution whose mean is the mean of the neighbors' random effects and variance proportional to the number of neighbors (formally, $v_i|v_j, j \in ne(i) ~ \mbox{Normal}(\bar{v_i}, \frac{\sigma^{2}_v}{m_j})$. Lastly, the BYM Spatiotemporal AR(1) (`spt`) adds an exchangeable random-effect ($\delta_i \sim Normal(0, \tau_\delta)$) for each period to allow for area-specific deviations in time trends.

>>>>

The BYM Spatial with AR(1) is the [Besag-York-Mollie (1991)](https://link.springer.com/article/10.1007/BF00116466){target="_blank"} intrinsic conditional autoregressive (ICAR) spatial model with AR(1) and exchangeable hyperparameters for the panel's temporal structure (referred to as `bym` using shorthand). The random-effect $v_i$ is assumed to come from a normal distribution whose mean is the mean of the neighbors' random effects and variance proportional to the number of neighbors (formally, $v_i|v_j, j \in ne(i) ~ \mbox{Normal}(\bar{v_i}, \frac{\sigma^{2}_v}{m_j})$. Lastly, the BYM Spatiotemporal AR(1) (`spt`) adds an exchangeable random-effect ($\delta_i \sim Normal(0, \tau_\delta)$) for each period to allow for area-specific deviations in time trends.
